---
title: "AI Prompting Experiment — Analysis Plan"
subtitle: "STAT 252 · Spring 2026 · Cal Poly SLO"
author: "Dr. Immanuel J. Williams & Sam Otto"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-title: "Research Questions"
    theme: cosmo
    code-fold: true
    code-summary: "Show code"
    number-sections: true
    highlight-style: github
    embed-resources: true
  pdf:
    toc: true
    number-sections: true
    colorlinks: true
execute:
  echo: true
  warning: false
  message: false
---

```{r setup}
library(tidyverse)
library(broom)
library(emmeans)
library(lme4)
library(car)
library(knitr)
library(kableExtra)
library(ggdist)
library(patchwork)

# ── Load data ────────────────────────────────────────────────────────────────
# Replace with your actual file path
# dat_raw <- read_csv("data/clean/analysis_dataset.csv")

# ── For development: simulate data matching your variable structure
set.seed(252)
n <- 90
dat_raw <- read_csv(here::here("data","combined_df.csv")) |> 
  mutate(
    pct_pre  = n_correct_pre  / 12,
    pct_post = n_correct_post / 11,
    group = as.character(group),
    group = factor(group,
                   levels = 1:3,
                   labels = c("No AI", "AI — No Structure", "Structured AI")),
    gain  = pct_post - pct_pre ,
    pct_gain = (gain / 100),
    section  = factor(section),
    Consent  = factor(Consent, levels = c(1L, 0L), labels = c("Consented", "Did Not Consent"))
  )
   




# # ── Consenting students only (primary analysis dataset) ──────────────────────
dat <- dat_raw |> filter(Consent == "Consented")

# # ── Color palette (Cal Poly) ──────────────────────────────────────────────────
pal <- c(
  "No AI"             = "#154734",   # Cal Poly green
  "AI — No Structure" = "#1A4E8C",   # blue
  "Structured AI"     = "#C69214"    # Cal Poly gold
)
```

---

# Overview

This document contains the full analysis plan for the STAT 252 Spring 2026 AI prompting experiment (IRB #2026-053). Students were randomly assigned to one of three conditions:

| Group ID | Condition | Description |
|:---:|---|---|
| 1 | No AI | Memory and handwritten notes only |
| 2 | AI — No Structure | Free ChatGPT Edu use, no format required |
| 3 | Structured AI (RTF) | ChatGPT Edu with Role · Task · Format prompting |

**Primary outcome:** Gain in quiz accuracy from pre-test to post-test (`n_correct_post − n_correct_pre`).

**Key variables:**

| Variable | Type | Description |
|---|---|---|
| `sis_id` | ID | Cal Poly student identifier |
| `n_correct_pre` | Integer (0–10) | Pre-test correct responses |
| `n_incorrect_pre` | Integer (0–10) | Pre-test incorrect responses |
| `n_correct_post` | Integer (0–10) | Post-test correct responses |
| `n_incorrect_post` | Integer (0–10) | Post-test incorrect responses |
| `section` | Categorical | Class section (01, 02, 03) |
| `Consent` | Binary | Whether student consented to participate |
| `group_id` | Integer (1–3) | Numeric group identifier |
| `group` | Categorical | Group label (No AI / AI No Structure / Structured AI) |

---

# Research Questions

## RQ1 — Baseline Distribution and Group Comparability

> **How does the distribution of pre-test performance vary across the three groups, and are there any baseline differences in student ability before the intervention?**

**Why this matters:** Random assignment should produce comparable groups at baseline. If pre-test scores differ meaningfully, any post-test differences are confounded by prior knowledge, not just the treatment. This question establishes whether the experiment is internally valid before any outcome analysis.

```{r rq1-descriptives-pre}
# ── Descriptive table ────────────────────────────────────────────────────────
dat |>
  group_by(group) |>
  summarise(
    n        = n(),
    mean_pre = round(mean(n_correct_pre), 2),
    sd_pre   = round(sd(n_correct_pre),   2),
    median   = median(n_correct_pre),
    min      = min(n_correct_pre),
    max      = max(n_correct_pre),
    .groups  = "drop"
  ) |>
  kable(
    caption = "Pre-test descriptive statistics by group",
    col.names = c("Group", "n", "Mean", "SD", "Median", "Min", "Max")
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```



```{r rq1-descriptives-post}
# ── Descriptive table ────────────────────────────────────────────────────────
dat |>
  group_by(group) |>
  summarise(
    n        = n(),
    mean_post = round(mean(n_correct_post, na.rm = TRUE), 2),
    sd_post   = round(sd(n_correct_post, na.rm = TRUE),   2),
    median   = median(n_correct_post, na.rm = TRUE),
    min      = min(n_correct_post, na.rm = TRUE),
    max      = max(n_correct_post, na.rm = TRUE),
    .groups  = "drop"
  ) |>
  kable(
    caption = "Post-test descriptive statistics by group",
    col.names = c("Group", "n", "Mean", "SD", "Median", "Min", "Max")
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```




```{r rq1-plot}
# ── Distribution plot ────────────────────────────────────────────────────────
dat |>
  ggplot(aes(x = group, y = n_correct_pre, fill = group, color = group)) +
  stat_halfeye(
    adjust = 0.8, width = 0.5, justification = -0.2,
    .width = 0, point_colour = NA, alpha = 0.6
  ) +
  geom_boxplot(
    width = 0.15, outlier.shape = NA, alpha = 0.8,
    position = position_nudge(x = 0.15)
  )  +
  scale_fill_manual(values = pal)  +
  scale_color_manual(values = pal) +
  scale_y_continuous(breaks = 0:15, limits = c(0, 15)) +
  coord_flip() +
  labs(
    title    = "RQ1: Pre-test Score Distribution by Group",
    subtitle = "Raincloud plot — consenting students only",
    x        = NULL,
    y        = "Number Correct (out of 10)",
    caption  = "STAT 252 · Spring 2026 · IRB #2026-053"
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "none",
        panel.grid.minor = element_blank())
```

```{r rq1-test}
# ── One-way ANOVA on pre-test scores ─────────────────────────────────────────
# H₀: μ_pre,1 = μ_pre,2 = μ_pre,3 (no baseline differences)
mod_pre <- aov(n_correct_pre ~ group, data = dat)
tidy(mod_pre) |>
  kable(digits = 4, caption = "One-way ANOVA on pre-test scores") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

**Interpretation guide:** A non-significant result (p > .05) supports group comparability at baseline. A significant result requires including `n_correct_pre` as a covariate in all subsequent analyses (ANCOVA approach).

---

## RQ2 — Post-test Outcomes Adjusted for Baseline

> **How do post-test outcomes differ across the three groups after adjusting for baseline pre-test performance, and does the Structured AI group demonstrate significantly greater learning gains compared to the other groups?**

**Why this matters:** Adjusting for pre-test performance removes the contribution of prior knowledge from the treatment effect estimate. This is the primary research question — it tests whether the treatment (and specifically RTF prompting) produced genuine learning beyond what was already known.

```{r rq2-ancova}
# ── ANCOVA: post ~ group + pre ────────────────────────────────────────────────
mod_ancova <- lm(n_correct_post ~ group + n_correct_pre, data = dat)

tidy(mod_ancova) |>
  kable(digits = 4, caption = "ANCOVA: Post-test ~ Group + Pre-test") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```



```{r rq2-emmeans}
# ── Estimated marginal means (adjusted for pre-test) ─────────────────────────
emm <- emmeans(mod_ancova, ~ group)
emm_df <- as.data.frame(emm)

emm_df |>
  kable(digits = 3, caption = "Adjusted group means (EMMs) from ANCOVA") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

```{r rq2-contrasts}
# ── Planned contrasts: Structured AI vs each other group ─────────────────────
contrast(emm, list(
  "Structured AI vs No AI"             = c(-1,  0,  1),
  "Structured AI vs AI No Structure"   = c( 0, -1,  1),
  "AI No Structure vs No AI"           = c(-1,  1,  0)
)) |>
  as.data.frame() |>
  kable(digits = 4, caption = "Planned pairwise contrasts (Structured AI as reference)") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

```{r rq2-plot}
# ── Adjusted means plot ───────────────────────────────────────────────────────
emm_df |>
  mutate(group = factor(group, levels = c("No AI", "AI — No Structure", "Structured AI"))) |>
  ggplot(aes(x = group, y = emmean, color = group)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.15, linewidth = 1) +
  scale_color_manual(values = pal) +
  scale_y_continuous(limits = c(0, 10), breaks = 0:10) +
  labs(
    title    = "RQ2: Adjusted Post-test Means by Group",
    subtitle = "Estimated marginal means \u00b1 95% CI, controlling for pre-test",
    x        = NULL,
    y        = "Adjusted Mean Correct (out of 10)"
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "none",
        panel.grid.minor = element_blank())
```

---

## RQ3 — Within-Section Improvement Rates by Group

> **Within each section, do students in different groups show different rates of improvement in accuracy from pre to post, and which group has the largest improvement?**

**Why this matters:** Students within a section share an instructor, classroom environment, and instructional delivery. If section confounds the group effect, improvement rates will differ across sections independently of treatment. This question checks whether the treatment effect is consistent across sections (generalizability) or section-dependent (interaction).

```{r rq3-section-descriptives}
# ── Gain by group × section ───────────────────────────────────────────────────
dat |>
  group_by(section, group) |>
  summarise(
    n         = n(),
    mean_gain = round(mean(gain, na.rm = TRUE), 2),
    sd_gain   = round(sd(gain, na.rm = TRUE),   2),
    .groups   = "drop"
  ) |>
  pivot_wider(
    id_cols    = section,
    names_from = group,
    values_from = c(mean_gain, sd_gain)
  ) |>
  kable(caption = "Mean gain score by section and group", digits = 2) |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

```{r rq3-plot}
# ── Gain distributions by section and group ───────────────────────────────────
dat |>
  ggplot(aes(x = group, y = gain, fill = group, color = group)) +
  geom_jitter(width = 0.15, alpha = 0.5, size = 1.5) +
  stat_summary(fun = mean, geom = "crossbar", width = 0.4,
               fatten = 2, color = "black", linewidth = 0.6) +
  facet_wrap(~ section) +
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal) +
  scale_y_continuous(breaks = -5:10) +
  labs(
    title    = "RQ3: Pre-to-Post Gain by Group Within Each Section",
    subtitle = "Black crossbar = group mean; dots = individual students",
    x        = NULL,
    y        = "Gain Score (post \u2212 pre)",
    fill     = NULL, color = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom",
        panel.grid.minor = element_blank(),
        strip.text = element_text(face = "bold"))
```

```{r rq3-interaction}
# ── Group × Section interaction model ────────────────────────────────────────
mod_section <- lm(gain ~ group * section, data = dat)
anova(mod_section) |>
  tidy() |>
  kable(digits = 4, caption = "ANOVA table: Gain ~ Group * Section") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

---

## RQ4 — Overall Improvement Rate (Consenting Students)

> **What was the overall rate of improvement for students who consented to the experiment, regardless of assigned group?**

**Why this matters:** This question characterizes the experiment-wide learning effect. It answers whether the activity itself — across all conditions — produced meaningful pre-to-post improvement. It also provides a summary statistic for reporting in the manuscript (e.g., "On average, consenting students improved by X points, representing a Y% increase in accuracy").

```{r rq4-overall}
# ── Overall summary ───────────────────────────────────────────────────────────
overall <- dat |>
  summarise(
    n           = n(),
    mean_pre    = round(mean(n_correct_pre/12, na.rm = TRUE),  2),
    mean_post   = round(mean(n_correct_post/11, na.rm = TRUE), 2),
    mean_gain   = round(mean(gain, na.rm = TRUE),           2),
    sd_gain     = round(sd(gain, na.rm = TRUE),            2),
    pct_gain    = round(mean(pct_gain, na.rm = TRUE) * 100, 1),
    n_improved  = sum(gain > 0, na.rm = TRUE),
    n_same      = sum(gain == 0, na.rm = TRUE),
    n_declined  = sum(gain < 0, na.rm = TRUE)
  )

overall |>
  pivot_longer(everything(), names_to = "Statistic", values_to = "Value") |>
  kable(caption = "Overall pre-to-post improvement — consenting students") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

```{r rq4-ttest}
# ── Paired t-test: is the mean gain significantly different from 0? ───────────
t.test(dat$gain, mu = 0, alternative = "greater") |>
  tidy() |>
  kable(digits = 4, caption = "One-sample t-test: H\u2080: mean gain = 0") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

```{r rq4-plot}
# ── Pre vs post plot for all consenting students ──────────────────────────────
dat |>
  select(sis_id, group, n_correct_pre, n_correct_post) |>
  pivot_longer(c(n_correct_pre, n_correct_post),
               names_to = "time",
               values_to = "score") |>
  mutate(time = factor(time,
                       levels = c("n_correct_pre", "n_correct_post"),
                       labels = c("Pre-test", "Post-test"))) |>
  ggplot(aes(x = time, y = score, group = sis_id, color = group)) +
  geom_line(alpha = 0.25) +
  geom_point(alpha = 0.4, size = 1.5) +
  stat_summary(aes(group = group), fun = mean, geom = "line",
               linewidth = 1.4, alpha = 0.9) +
  stat_summary(aes(group = group), fun = mean, geom = "point",
               size = 3.5) +
  scale_color_manual(values = pal) +
  scale_y_continuous(limits = c(0, 10), breaks = 0:10) +
  labs(
    title    = "RQ4: Individual and Group-Level Pre-to-Post Trajectories",
    subtitle = "Thin lines = individual students; thick lines = group means",
    x        = NULL,
    y        = "Number Correct (out of 10)",
    color    = "Group"
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom",
        panel.grid.minor = element_blank())
```

---

## RQ5 — Consent Bias and Self-Selection Threat

> **Do students who consented to participate differ from those who did not on pre-test performance, and does consent status represent a threat to the internal validity of the study?**

**Why this matters:** If students who chose to consent scored systematically higher (or lower) on the pre-test than non-consenters, then the consenting sample is not representative of the full class. This is a self-selection threat. Demonstrating that consenters and non-consenters are comparable at baseline strengthens the argument that findings generalize to the broader student population and that the consenting group is not an unusual subset.

```{r rq5-consent-comparison}
# ── Pre-test comparison: consented vs did not consent ─────────────────────────
dat_raw |>
  group_by(Consent) |>
  summarise(
    n        = n(),
    mean_pre = round(mean(n_correct_pre), 2),
    sd_pre   = round(sd(n_correct_pre),   2),
    .groups  = "drop"
  ) |>
  kable(caption = "Pre-test scores: consented vs. did not consent") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

```{r rq5-test}
# ── Welch t-test: consent group pre-test difference ───────────────────────────
t.test(n_correct_pre ~ Consent, data = dat_raw) |>
  tidy() |>
  kable(digits = 4, caption = "Welch t-test: pre-test by consent status") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

```{r rq5-plot}
dat_raw |>
  ggplot(aes(x = Consent, y = n_correct_pre, fill = Consent)) +
  geom_boxplot(alpha = 0.7, width = 0.4, outlier.shape = NA) +
  geom_jitter(width = 0.12, alpha = 0.4, size = 1.8) +
  scale_fill_manual(values = c("Consented" = "#154734", "Did Not Consent" = "#CCCCCC")) +
  labs(
    title    = "RQ5: Pre-test Performance by Consent Status",
    subtitle = "Assessing self-selection threat to internal validity",
    x        = NULL,
    y        = "Number Correct — Pre-test (out of 10)"
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "none",
        panel.grid.minor = element_blank())
```

---

## RQ6 — Section as a Confounding Variable

> **Does class section independently predict post-test performance after accounting for group assignment and pre-test scores, and should section be included as a blocking factor in the primary analysis?**

**Why this matters:** Students were assigned to groups within sections, meaning section membership is entangled with group membership. If the instructor's delivery, classroom environment, or section composition creates systematic differences in learning, those differences could masquerade as treatment effects. This question determines whether section needs to be modeled explicitly — either as a fixed effect (if sections differ in ways we care about) or as a random effect (if we treat sections as a sample from a larger population of sections).

```{r rq6-section-means}
# ── Section-level descriptives ────────────────────────────────────────────────
dat |>
  group_by(section) |>
  summarise(
    n         = n(),
    mean_pre  = round(mean(n_correct_pre),  2),
    mean_post = round(mean(n_correct_post), 2),
    mean_gain = round(mean(gain),           2),
    .groups   = "drop"
  ) |>
  kable(caption = "Performance by section (all groups combined)") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

```{r rq6-models}
# ── Compare models with and without section ───────────────────────────────────

# Model 1: group + pre only
m1 <- lm(n_correct_post ~ group + n_correct_pre, data = dat)

# Model 2: group + pre + section (section as fixed effect)
m2 <- lm(n_correct_post ~ group + n_correct_pre + section, data = dat)

# Model 3: mixed model — section as random effect
m3 <- lmer(n_correct_post ~ group + n_correct_pre + (1 | section), data = dat)

# Model comparison
anova(m1, m2) |>
  tidy() |>
  kable(digits = 4, caption = "LRT: does adding section improve fit?") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

**Decision rule:** If the LRT is significant (p < .05), include section as a covariate in the primary analysis (RQ2). If not, the simpler model without section is preferred for parsimony.

---

## RQ7 — Ceiling and Floor Effects

> **Do students who scored at or near the ceiling on the pre-test (8–10 correct) show attenuated gain scores compared to lower-scoring students, and does this ceiling effect differ across groups?**

**Why this matters:** A 10-item quiz has limited range. Students who already scored 9 or 10 on the pre-test have almost no room to improve — their gains will be near zero regardless of treatment. If one group happened to have more high pre-test scorers, that group will appear to show less improvement even if the treatment was equally effective. Identifying ceiling effects validates the sensitivity of the assessment instrument and informs interpretation of the gain score results.

```{r rq7-ceiling}
# ── Classify students by pre-test performance band ────────────────────────────
dat <- dat |>
  mutate(pre_band = case_when(
    n_correct_pre <= 3  ~ "Low (0\u20133)",
    n_correct_pre <= 6  ~ "Mid (4\u20136)",
    n_correct_pre <= 8  ~ "High (7\u20138)",
    TRUE                ~ "Near ceiling (9\u201310)"
  ) |> factor(levels = c("Low (0\u20133)", "Mid (4\u20136)",
                          "High (7\u20138)", "Near ceiling (9\u201310)")))

dat |>
  group_by(pre_band, group) |>
  summarise(
    n         = n(),
    mean_gain = round(mean(gain), 2),
    .groups   = "drop"
  ) |>
  pivot_wider(names_from = group, values_from = c(n, mean_gain)) |>
  kable(caption = "Mean gain by pre-test performance band and group") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

```{r rq7-plot}
dat |>
  ggplot(aes(x = n_correct_pre, y = gain, color = group)) +
  geom_jitter(width = 0.2, height = 0.1, alpha = 0.5, size = 1.8) +
  geom_smooth(method = "lm", se = TRUE, linewidth = 1.2, alpha = 0.15) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  scale_color_manual(values = pal) +
  scale_x_continuous(breaks = 0:10) +
  scale_y_continuous(breaks = -5:10) +
  facet_wrap(~ group) +
  labs(
    title    = "RQ7: Gain Score by Pre-test Score — Ceiling Effect Check",
    subtitle = "Negative slope suggests ceiling compression at high pre-test values",
    x        = "Pre-test Score (number correct)",
    y        = "Gain Score (post \u2212 pre)",
    color    = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        strip.text = element_text(face = "bold"))
```

---

## RQ8 — Prior Knowledge × Treatment Interaction

> **Does the relationship between prior knowledge (pre-test score) and post-test performance differ across the three groups, suggesting that certain students benefit more from AI-assisted study depending on their baseline ability?**

**Why this matters:** Treatment effects in educational research are rarely uniform — students with different prior knowledge often respond differently to the same intervention. A positive interaction between prior knowledge and the Structured AI condition would mean that higher-ability students benefit more from RTF prompting (expertise advantage). A negative interaction would mean lower-ability students benefit more (scaffolding advantage). This finding has direct implications for how AI prompting tools should be deployed and for whom.

```{r rq8-interaction-model}
# ── Prior knowledge × group interaction ───────────────────────────────────────
mod_interact <- lm(n_correct_post ~ group * n_correct_pre, data = dat)

tidy(mod_interact) |>
  kable(digits = 4, caption = "Model: Post ~ Group * Pre-test (interaction)") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

# Compare to additive model
anova(mod_ancova, mod_interact) |>
  tidy() |>
  kable(digits = 4, caption = "LRT: additive vs. interaction model") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

```{r rq8-plot}
# ── Predicted post-test by pre-test for each group ────────────────────────────
pred_grid <- expand_grid(
  group         = levels(dat$group),
  n_correct_pre = 0:10
) |>
  mutate(group = factor(group, levels = levels(dat$group)))

pred_grid$n_correct_post <- predict(mod_interact, newdata = pred_grid)

pred_grid |>
  ggplot(aes(x = n_correct_pre, y = n_correct_post, color = group)) +
  geom_line(linewidth = 1.4) +
  geom_jitter(data = dat,
              aes(x = n_correct_pre, y = n_correct_post, color = group),
              width = 0.15, height = 0.1, alpha = 0.35, size = 1.5) +
  scale_color_manual(values = pal) +
  scale_x_continuous(breaks = 0:10) +
  scale_y_continuous(limits = c(0, 10), breaks = 0:10) +
  labs(
    title    = "RQ8: Prior Knowledge \u00d7 Treatment Interaction",
    subtitle = "Non-parallel lines indicate differential benefit by prior knowledge",
    x        = "Pre-test Score (number correct)",
    y        = "Predicted Post-test Score (number correct)",
    color    = "Group"
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom",
        panel.grid.minor = element_blank())
```

---

# Summary of Analyses

| RQ | Primary Test | Key Variables | Decision Criterion |
|:---:|---|---|---|
| 1 | One-way ANOVA | `n_correct_pre ~ group` | p < .05 flags baseline imbalance |
| 2 | ANCOVA + contrasts | `n_correct_post ~ group + n_correct_pre` | EMM contrast: Structured AI vs others |
| 3 | Group × Section interaction | `gain ~ group * section` | Significant interaction = inconsistent effect |
| 4 | Paired t-test | `gain ~ 1` (H₀: μ=0) | p < .05 = evidence of learning |
| 5 | Welch t-test | `n_correct_pre ~ Consent` | Non-significant = no selection bias |
| 6 | LRT (nested models) | `post ~ group + pre` vs `+ section` | Significant = include section as covariate |
| 7 | Descriptive + regression | `gain ~ n_correct_pre` by group | Negative slope = ceiling effect present |
| 8 | Interaction LRT | `post ~ group * pre` vs additive | Significant = effect depends on prior knowledge |

---

# Session Info

```{r session-info}
sessionInfo()
```
