---
title: "Experiment Completion Score"
format:
  html:
    toc: true
    df-print: paged
execute:
  echo: true
  warning: false
  message: false
---

## Purpose

This file checks which students completed the pre-test and post-test for the experiment. The roster is treated as the official list of students. A student receives 5 points if they completed at least one of the two tests.

## Load packages

```{r}
library(here)
library(readr)
library(readxl)
library(dplyr)
library(janitor)
library(stringr)
```

## File paths

```{r}
pre_test_path <- here(
  "data",
  "Pre-Test - Experiment Quiz Student Analysis Report.csv"
)

post_test_path <- here(
  "data",
  "Post-Test - Experiment Quiz Student Analysis Report.csv"
)

roster_path <- "/Users/immanuelwilliams/Library/CloudStorage/OneDrive-Personal/Documents/Important_Files/Cal_Poly/01_Class_Material/STAT_252/stat252-spring-2026/Data/roster/stat252_spring_2026_roster_new.xlsx"
```

## Load data

```{r}
pre_test_raw <- read_csv(pre_test_path, show_col_types = FALSE) |>
  clean_names()

post_test_raw <- read_csv(post_test_path, show_col_types = FALSE) |>
  clean_names()

roster_raw <- read_excel(roster_path) |>
  clean_names()
```

## Check column names

Use this section to verify that each file has a `sis_id` column after cleaning the names.

```{r}
names(pre_test_raw)
names(post_test_raw)
names(roster_raw)
```

## Clean student IDs

```{r}
clean_sis_id <- function(x) {
  as.character(as.numeric(x))
}

pre_test <- pre_test_raw |>
  mutate(
    sis_id = clean_sis_id(sis_id) |> str_trim()
  ) |>
  select(name, sis_id) |> 
  filter(!is.na(sis_id), sis_id != "") |>
  distinct(sis_id) |>
  mutate(completed_pre_test = TRUE) 

post_test <- post_test_raw |>
  mutate(
    sis_id = clean_sis_id(sis_id) |> str_trim()
  ) |>
  select(name, sis_id) |> 
  filter(!is.na(sis_id), sis_id != "") |>
  distinct(sis_id) |>
  mutate(completed_post_test = TRUE)

roster <- roster_raw |>
  mutate(
    sis_id = clean_sis_id(sis_id) |> str_trim()
  ) |>
  filter(!is.na(sis_id), sis_id != "")
```

## Create completion and score data frame

```{r}
completion_score_df <- roster |>
  left_join(pre_test, by = "sis_id") |>
  left_join(post_test, by = "sis_id") |>
  mutate(
    completed_pre_test = if_else(is.na(completed_pre_test), FALSE, completed_pre_test),
    completed_post_test = if_else(is.na(completed_post_test), FALSE, completed_post_test),
    completed_at_least_one = completed_pre_test | completed_post_test,
    score = if_else(completed_at_least_one, 5, 0)
  ) 
  
  
score_df <- completion_score_df |>
  select(email,score)


```

## Completion summary

```{r}
completion_summary <- completion_score_df |>
  summarize(
    n_students_on_roster = n(),
    n_completed_pre_test = sum(completed_pre_test),
    n_completed_post_test = sum(completed_post_test),
    n_completed_at_least_one = sum(completed_at_least_one),
    n_completed_both = sum(completed_pre_test & completed_post_test),
    n_completed_neither = sum(!completed_pre_test & !completed_post_test),
    total_points_awarded = sum(score)
  )

completion_summary
```

## Students who did not complete either test

```{r}
missing_both_df <- completion_score_df |>
  filter(!completed_pre_test, !completed_post_test)

missing_both_df
```

## Save output

```{r}
write_csv(
  score_df,
  here("data", "cci_9_score.csv")
)

write_csv(
  missing_both_df,
  here("data", "students_missing_both_tests.csv")
)
```
