---
title: "Pre/Post Test Score Join — STAT 252 Spring 2026"
author: "Dr. Immanuel J. Williams"
date: today
format:
  html:
    toc: true
    toc-depth: 2
    theme: cosmo
    embed-resources: true
execute:
  echo: true
  warning: false
  message: false
---

## Setup

```{r}
#| label: load-packages

library(tidyverse)
library(readxl)
library(here)
library(janitor)
```

## 1. Read Data

### Quiz CSVs

```{r}
#| label: read-quiz-data

pre_raw <- read_csv(
  "data/Pre-Test - Experiment Quiz Student Analysis Report.csv",
  show_col_types = FALSE
)

post_raw <- read_csv(
  "data/Post-Test - Experiment Quiz Student Analysis Report.csv",
  show_col_types = FALSE
)
```

### Roster Files

```{r}
#| label: read-roster

roster_raw <- read_xlsx(
  "/Users/immanuelwilliams/Library/CloudStorage/OneDrive-Personal/Documents/Important_Files/Cal_Poly/01_Class_Material/STAT_252/stat252-spring-2026/Data/roster/stat252_spring_2026_roster_new.xlsx"
)

consent_confirmed <- read_xlsx(here("data", "consent_confirmed.xlsx"))
no_identi_roster  <- read_xlsx(here("data", "no_identification_roster.xlsx"))
```

---

## 2. Build Anonymized Roster (`analysis_df`)

Inner join `consent_confirmed` and `no_identi_roster` by `section` and `row`,
then drop all personally identifiable columns.

```{r}
#| label: build-analysis-df

joined_df <- inner_join(
  consent_confirmed,
  no_identi_roster,
  by = c("section", "row")
)

analysis_df <- joined_df |>
  select(-student_name, -email)
```

---

## 3. Extract and Rename Quiz Columns

```{r}
#| label: extract-scores

pre_scores <- pre_raw |>
  clean_names() |>
  select(sis_id, n_correct, n_incorrect) |>
  rename(
    n_correct_pre   = n_correct,
    n_incorrect_pre = n_incorrect
  )

post_scores <- post_raw |>
  clean_names() |>
  select(sis_id, n_correct, n_incorrect) |>
  rename(
    n_correct_post   = n_correct,
    n_incorrect_post = n_incorrect
  )
```

---

## 4. Standardize `sis_id` as Character

```{r}
#| label: coerce-sis-id

clean_sis_id <- function(x) {
  as.character(as.numeric(x))
}

pre_scores <- pre_scores |>
  mutate(sis_id = clean_sis_id(sis_id))

post_scores <- post_scores |>
  mutate(sis_id = clean_sis_id(sis_id))

roster <- roster_raw |>
  clean_names() |>
  mutate(sis_id = clean_sis_id(sis_id)) |>
  select(sis_id, row)

analysis_df <- analysis_df |>
  mutate(sis_id = clean_sis_id(sis_id))
```

---

## 5. Join All Data Frames

Start from the roster, bring in pre- and post-test scores, then attach
anonymized metadata from `analysis_df`. Drop `row` from `analysis_df` before
joining to avoid a duplicate column conflict with the one already in `roster`.

```{r}
#| label: join-data

combined <- roster |>
  left_join(pre_scores,  by = "sis_id") |>
  left_join(post_scores, by = "sis_id") |>
  left_join(
    select(analysis_df, -row),
    by = "sis_id"
  ) |>
  select(
    sis_id,
    section,
    row,
    n_correct_pre,
    n_incorrect_pre,
    n_correct_post,
    n_incorrect_post,
    everything()
  )

glimpse(combined)
write.csv(combined,here("data","combined_df.csv"), row.names = FALSE)
```

---

## 6. Preview

```{r}
#| label: preview

combined |>
  head(10) |>
  knitr::kable(caption = "First 10 rows of joined dataset")
```

---

## 7. Summary of Missing Values

```{r}
#| label: missing-check

combined |>
  summarise(
    n_total              = n(),
    missing_pre_correct  = sum(is.na(n_correct_pre)),
    missing_post_correct = sum(is.na(n_correct_post))
  ) |>
  knitr::kable(caption = "Missing value summary")
```
